%%
%% This is file `thesis-ex.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% uiucthesis2014.dtx  (with options: `example')
%% 
\def\fileversion{v2.25b} \def\filedate{2014/05/02}
%% Package and Class "uiucthesis2014" for use with LaTeX2e.
\documentclass[edeposit,fullpage]{uiucthesis2014}

\usepackage{url}

\usepackage{graphicx,mathtools}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage[hidelinks=true]{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    allcolors={blue}
}
\usepackage{graphicx}
%\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{filecontents}
\usepackage{amsthm,array}
\newcommand{\code}[1]{\texttt{#1}}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}

\newcommand{\NA}{\centering{---}}
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
  
 \usepackage{balance}

\newtheorem{mydef}{Definition}
\newcolumntype{K}[1]{>{\centering\arraybackslash}p{#1}}

\newcommand\blank[1]{\rule[-.2ex]{#1}{.4pt}} 

\usetikzlibrary{patterns}
\usepackage{amssymb,bbm,amsmath,url,enumitem,makecell}
\usepackage{multirow,amsmath,pgfplots,adjustbox,wasysym,marvosym}
\usepackage[position=top]{subfig}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\usepgfplotslibrary{groupplots}
\usetikzlibrary{patterns}
\usepackage[ruled,linesnumbered]{algorithm2e}

\newcommand{\correcttexttt}[1]{{\fontfamily{pcr}\selectfont#1}} 

\begin{document}

\title{Data-Driven Assistance for User Decision Making on Mobile Devices}
\author{Susan Xueqing Liu}
\department{Computer Science}
\schools{B.A., University of Columbia, 1981\\
         A.M., University of Illinois at Urbana-Champaign, 1986}
\phdthesis
\advisor{ChengXiang Zhai, Tao Xie}
\degreeyear{2019}
\committee{Professor ChengXiang Zhai, Chair\\Professor Tao Xie, Director of Dissertation\\Professor Carl Gunter\\Associate Professor William Enck}
\maketitle

\frontmatter

%% Create an abstract that can also be used for the ProQuest abstract.
%% Note that ProQuest truncates their abstracts at 350 words.
\begin{abstract}

Mobile devices are ubiquitous in people's lives. As mobile users are expected to exceed 4.5 billion in 2019, mobile devices frequently support users to conduct decision making tasks such as shopping and business decisions. Meanwhile, mobile users must also have to make decisions on the permissions to their personal data, e.g., location contact lists. It is therefore important to ensure that users can successfully make such decisions. 

However, user experience on decision making on mobile devices would be affected by the physical characteristics of mobile devices: they are small and it is difficult to type on these devices. Further more, both editing and navigation would be harder than that on computers. Such conditions may further amplify the commonly existed knowledge gap in decision making processes. With the reduced capability to query and edit, users thus explore less options and it is less likely for them to find the optimal option if it is not easy to find. Statistics show that during shopping, users often explore options first on mobile devices, and later switch to computer when they make the final decision. Can we make it very easy to make decisions on mobile devices? The key of assisting user decision making is to bridge the knowledge gap, for which we can provide external knowledge extracted from a large dataset using machine learning, data mining or information retrieval techniques. 

This thesis studies three important real-world decision making problems for users on mobile devices: mobile shopping decisions (Chapter~\ref{ch2:shopping}), security decisions (Chapter~\ref{ch3:runtime} and Chapter~\ref{ch4:clap}), and business decisions with mobile business intelligence tools such as Microsoft Power BI (Chapter~\ref{ch5:nl2sql}). In each problem, we explore how to use three different strategies to bridge the knowledge gap: first, using summarization to allow the user to navigate the large database and explore ways for finding the optimal option (Chapter~\ref{ch2:shopping}), second, using crowd sourced decisions from similar examples to explain a blackbox operation (Chapter~\ref{ch3:runtime} and Chapter~\ref{ch4:clap}), and finally, using translation to bridge the gap between novice user and a technical domain (Chapter~\ref{ch5:nl2sql}). Finally, Chapter~\ref{ch6:conclusion} summarizes the remaining challenges, discusses the future work and draws the conclusion.

\end{abstract}

%% Create a dedication in italics with no heading, centered vertically
%% on the page.
% \begin{dedication}
% To Father and Mother.
% \end{dedication}

%% Create an Acknowledgements page, many departments require you to
%% include funding support in this.
% \chapter*{Acknowledgments}

% This project would not have been possible without the support of
% many people. Many thanks to my adviser, Lawrence T. Strongarm, who
% read my numerous revisions and helped make some sense of the
% confusion. Also thanks to my committee members, Reginald Bottoms,
% Karin Vegas, and Cindy Willy, who offered guidance and support.
% Thanks to the University of Illinois Graduate College for awarding
% me a Dissertation Completion Fellowship, providing me with the
% financial means to complete this project. And finally, thanks to
% my husband, parents, and numerous friends who endured this long
% process with me, always offering support and love.

%% The thesis format requires the Table of Contents to come
%% before any other major sections, all of these sections after
%% the Table of Contents must be listed therein (i.e., use \chapter,
%% not \chapter*).  Common sections to have between the Table of
%% Contents and the main text are:
%%
%% List of Tables
%% List of Figures
%% List Symbols and/or Abbreviations
%% etc.

\tableofcontents
\listoftables
\listoffigures

%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
\chapter{List of Abbreviations}

% \begin{symbollist*}
% \item[CA] Caffeine Addict.
% \item[CD] Coffee Drinker.
% \end{symbollist*}

%% Create a List of Symbols. The left column
%% is 0.7 inch wide and centered
\chapter{List of Symbols}

% \begin{symbollist}[0.7in]
% \item[$\tau$] Time taken to drink one cup of coffee.
% \item[$\mu$g] Micrograms (of caffeine, generally).
% \end{symbollist}

\mainmatter

\input{tex/1-intro/1-intro}

\input{tex/2-shopping/2-shopping}

\input{tex/3-runtime/3-runtime}

\input{tex/4-clap/4-clap}

\input{tex/5-nl2sql/5-nl2sql}

\input{tex/6-conclusion/6-conclusion}

\appendix*

\include{Appendix.tex}

\backmatter

\bibliographystyle{apalike}
\bibliography{thesisbib}

\end{document}
\endinput
%%
%% End of file `thesis-ex.tex'.
