%!TEX root =../../thesis-ex.tex

\chapter{Introduction}

With the rise of mobile devices, more than 70\% of the world population now own a mobile devices. Different from larger devices, users can easily carry these small devices on the go and perform different tasks such as searching for local restaurants, browsing news, replying emails, learning new languages, etc. Based on the statistics, mobile device subscription has surpassed that of laptop since 2016. As a result, more users access information on mobile devices rather than on desktops. Statistics show that in average, American adults spend approximately 4 hours a day interacting with their phones. Many of today's startup companies starts from mobile application and then move up to larger devices, because the mobile platform allows them to grow the business faster, i.e., mobile-first and mobile-only strategies. 

As a result, it is a critical task for business owners to make sure that user experience on mobile devices are friendly and user can effectively interact with information. In this thesis, we take the look at one problem in user interaction: users' decision making task on mobile devices. Due to the large number of mobile subscription, there has to be many cases where users need to make decisions and where their mobile devices are the only tool they can rely on. For example, consider a user traveling without the laptop and it happens to be Amazon Prime day where many products are on sale, or no Wi-Fi is available. With mobile devices, it is more convenient for them to catch the deals because if they need to wait until the desktop is available, they might have missed the deal. 

With the physical characteristics, however, it would be more difficult for the users to perform information seeking activities on mobile devices. Mobile screens are small and it is more difficult to type, edit or navigate on these devices. As a result, mobile devices are often where the users first research for a product. For example, after seeing an advertisement, they may become interested in buying a product and then start searching. Then they often end up buying it on their computers. Arguably, today it would still be more convenient to search and buy products on a computer. However, if we can improve users' buying experience on their phones, perhaps that makes them feel safer to make the decision over the phones, e.g., without having to miss the Prime day deal. 

How to improve users' decision making experience on their mobile devices? One key factor that determines decision making is how much information the user knows about the options. That said, decisions are frequently made out of uncertainty. Consider again the shopping example, which one is the optimal deal for the users' need? Theoretically speaking, the user can only know if for sure if she can traverse all the deals. However, on Prime day Amazon there might be millions of deals, so it is impossible to traverse them all. With keywords search, the user can browse through the top ranked items, but due to the screen size, difficulty for typing, etc., users would be more biased towards selecting the top ranked items, making it more likely for the user to make a suboptimal decision. 

Generally, the difficulty for users to reach the optimal shopping decision is caused by the knowledge gap between the user and the complete information that is required for decision making. The knowledge gap is a general problem that almost always exist with decision making. On mobile devices, this problem is further amplified by the difficulty for typing, editing, etc. Other decision making tasks on mobile devices include making business decisions (with business intelligence tools) and making security decisions by interacting with Android permission system. Similar as shopping, in both cases there exist knowledge gap which causes the difficulty in decision making. 

One approach for assisting users with decision making is to bridge the knowledge gap by supporting knowledge that the user potentially need to refer to for decision making. Compared with automated decision making, this approach would then be more friendly and explainable. The rapid growth of mobile industry has given rise to mobile data copora, e.g., 2.7 million apps are published on Android play store. Such datasets, as well as other mobile-related data (e.g., user mobile search data) provides an opportunity to support user decision making using data-driven approaches such as data mining, machine learning and information retrieval. In this thesis, we argue that \textbf{the massive and growing mobile-related meta datasets as well as user-generated data can be leveraged to computationally support user decision making by extracting such knowledge from these datasets}. 

This chapter is organized as follows. Section~\ref{ch1:sec1:background} introduces background and existing work on decision making support and mobile user interaction. Section~\ref{ch1:sec2:motiv} presents the motivation of this thesis. Finally, Section~\ref{ch1:sec3:overview} describes the organization of this thesis and summarizes each individual piece of work. 

\input{tex/1-intro/1-motiv}

\input{tex/1-intro/1-background}

\input{tex/1-intro/1-overview}